\documentclass[a4paper,11pt]{article}

% Package imports
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\usepackage{fontawesome5}

% Color definitions
\definecolor{darkblue}{RGB}{0,0,139}

% Page layout
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
\setlength{\footskip}{5pt} % Addressing fancyhdr warning

% Hyperlink setup (moved after fancyhdr to address warning)
\usepackage[hidelinks]{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,
    urlcolor=darkblue,
}

% Custom box settings
\usepackage[most]{tcolorbox}
\tcbset{
    frame code={},
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!20,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=-2mm,
    boxsep=4pt,
    arc=0pt,outer arc=0pt,
}

% URL style
\urlstyle{same}

% Text alignment
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\circ$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm,itemsep=0.5mm]}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%

% Commands for icon sizing and positioning
\newcommand{\socialicon}[1]{\raisebox{-0.05em}{\resizebox{!}{1em}{#1}}}
\newcommand{\ieeeicon}[1]{\raisebox{-0.3em}{\resizebox{!}{1.3em}{#1}}}

% Font options
\newcommand{\headerfonti}{\fontfamily{phv}\selectfont} % Helvetica-like (similar to Arial/Calibri)
\newcommand{\headerfontii}{\fontfamily{ptm}\selectfont} % Times-like (similar to Times New Roman)
\newcommand{\headerfontiii}{\fontfamily{ppl}\selectfont} % Palatino (elegant serif)
\newcommand{\headerfontiv}{\fontfamily{pbk}\selectfont} % Bookman (readable serif)
\newcommand{\headerfontv}{\fontfamily{pag}\selectfont} % Avant Garde-like (similar to Trebuchet MS)
\newcommand{\headerfontvi}{\fontfamily{cmss}\selectfont} % Computer Modern Sans Serif
\newcommand{\headerfontvii}{\fontfamily{qhv}\selectfont} % Quasi-Helvetica (another Arial/Calibri alternative)
\newcommand{\headerfontviii}{\fontfamily{qpl}\selectfont} % Quasi-Palatino (another elegant serif option)
\newcommand{\headerfontix}{\fontfamily{qtm}\selectfont} % Quasi-Times (another Times New Roman alternative)
\newcommand{\headerfontx}{\fontfamily{bch}\selectfont} % Charter (clean serif font)

\begin{document}
\headerfontiii

% Header
\begin{center}
    {\Huge\textbf{Virendra Carpenter}}
\end{center}
\vspace{-6mm}

\begin{center}
    \small{
    +917724855355 | \href{mailto:virendracarpenter28@gmail.com}{virendracarpenter28@gmail.com} | 
    \href{https://vcarp.vercel.app/}{vcarp.vercel.app}
    }
\end{center}
\vspace{-6mm}

\begin{center}
    \small{
    \socialicon{\faLinkedin} \href{https://www.linkedin.com/in/virendracarpenter/}{virendracarpenter} | 
    \socialicon{\faGithub} \href{https://github.com/virendracarpenter}{virendracarpenter} | 
    % \socialicon{\faCode} \href{https://leetcode.com/vcarp}{vcarp} |
    \socialicon{\faTwitter} \href{https://twitter.com/veecarpenter}{veecarpenter}
    }
\end{center}
\vspace{-6mm}
\begin{center}
    \small{Shukliya, Indore - 301233, India}
\end{center}

\vspace{-4mm}

\section{\textbf{Objective}}
\vspace{1mm}
\small{
  Python developer with 1.6+ years experience in building scalable applications with Django and REST APIs, eager to drive innovative solutions and collaborate on high-quality software.
}
\vspace{-2mm}


\section{\textbf{Skills}}
\vspace{-0.2mm}
  \resumeHeadingSkillStart
    \resumeSubItem{Programming Languages:}
      {Python, JavaScript, SQL, HTML, CSS}
    \resumeSubItem{Frameworks And Libraries:}
      {Django, Django Rest Framework, FastAPI, Flask, Wagtail, WebSockets, Bootstrap, Ajax,  jQuery, OpenAI API, Prompt Engineering, Beautiful Soup, Selenium, Celery, Redis, Pandas, NumPy, Matplotlib}
    \resumeSubItem{Database Systems:}
      {PostgreSQL, SQLite, MySQL, AWS RDS, GCP SQL Instance}
    \resumeSubItem{Version Control \& Cloud Technologies:}
      {Git, GitHub, Docker, Nginx, Uvicorn, Gunicorn, Github Actions, AWS (Lambda, S3, EC2, RDS, Secret Manager), GCP (Compute Engine, Document AI, Load Balancer, App Engine, Storage Bucket)}
    \resumeSubItem{Other Tools \& Technologies:}
      {PyCharm, Vim, Postman, Shell Scripting,  Zoho CRM}
  \resumeHeadingSkillEnd


\section{\textbf{Profrssional Experience}}
\vspace{-0.4mm}
  \resumeSubHeadingListStart
  \resumeSubheading
      {{Cyber Infrastructure (P) Ltd [\href{https://www.cisin.com/}{\faIcon{globe}}]}}{Indore, India}
      {Software Engineer}{April 2023 - Present}
      \resumeItemListStart
        \item Designed and implemented scalable system architectures for multiple projects. Developed backend functionalities using Python, Django, and DRF, integrating trading algorithms and automated quiz generation. 
        \item Deployed and managed applications on AWS (EC2, S3) using Docker for containerization, streamlining continuous integration and deployment processes while ensuring high availability and scalability.
        \item Worked closely with the business team to understand and fulfill client requirements. Analyzed client requirements, conducted RD, and provided accurate project estimates and responses.
        \item Collaborated with cross-functional teams to deliver features and optimize performance. Facilitated clear communication with global clients, ensuring project success and satisfaction.
      \resumeItemListEnd 
  \resumeSubHeadingListEnd
\vspace{-6mm}


\section{\textbf{Projects}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeProject
  {Hands-Free Trading: Trading Automation}
  {Tools: Python3, Django, Django Rest Framework, WebSockets, Kafka, React, PostgreSQL, Microservices, AWS (RDS, ECR, ECS, S3), Docker}
  {}{}
  % {{}[\href{https://}{\textcolor{darkblue}{\faGlobe}}]}
\resumeItemListStart
  \item Microservices Architecture: Developed a cloud-based algo-trading platform architected with microservices. Created RESTful APIs for inter-service communication and implemented an API gateway. Integrated brokers (e.g., Tradier, Tradestation) and developed secure user management (JWT, Google Auth).
  \item Improved perfomance by 30 \%, by utilized Celery for caching and deployed on AWS (RDS, ECR, ECS) for scalability. Designed services for notifications, signal trade engine, cronjobs and payments. Implemented CI/CD pipelines, leveraging PostgreSQL, Gunicorn, and Nginx for robust performance.
\resumeItemListEnd

\resumeProject
  {MySportsDriver Chatbot: A website assistant bot for MySportsDriver platform.}
  {Tools: Python3, FastAPI, OpenAI API, Bootstrap, HTML, CSS, JavaScript, Ajax, Uvicorn, AWS, Docker, Zoho CRM, Nginx}
  {}{}
  % {{}[\href{https://}{\textcolor{darkblue}{\faGlobe}}]}
\resumeItemListStart
  \item Developed a chatbot using FastAPI and OpenAI to assist users with predefined Q\&A and handle dynamic queries based on user input. Implemented feedback mechanism for user satisfaction and integrated ticket generation in Zoho CRM for unresolved queries.
  \item Applied prompt engineering techniques to improve the chatbot's ability to interpret user queries and provide accurate responses.
\resumeItemListEnd

\resumeProject
  {Starlight: A Quiz Management System}
  {Tools: Python3, Django, GCP, PostgreSQL, Docker, Bootstrap, HTML, CSS, JavaScript, Ajax, OpenAI, Rasa}
  {}{}
  % {{}[\href{https://}{\textcolor{darkblue}{\faGlobe}}]}
\resumeItemListStart
  \item Full-Stack Development: Developed a web-based quiz platform, supporting various question types (MCQs, true/false, fill-in-the-blank, equations, and formulas). Integrated Google Sheets for bulk question uploads and implemented AI-powered automatic question generation from PDFs or specific topics via OpenAI for teachers.
  \item Implemented a custom Rasa chatbot for interactive quizzes, including a dino game for engagement.
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-6mm}


\section{\textbf{Additional Information}}
\vspace{-0.4mm}
\small{
\textbf{Languages:}  English, Hindi

\textbf{Interests:} Technology Trends,  Customising System , Hiking
}

\vspace{-4mm}


\section{\textbf{Education}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeSubheading
{Bachelor of Technology, Computer Science and Engineering}{Indore, India}
{IPS Academy, Institute of Engineering \& Science}{2019 - 2023}
\resumeItemListStart
\item CGPA: 8.61/10.00
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-6mm}

\end{document}